Old is Still Gold: A Comparison of Cyber and Regular Consumer Fraud in The United States

### 2017-01-18 paper/paper.tex
reworked concl

\begin{figure}[b]
\centering
  \includegraphics[scale=0.29]{graphics/demographics.pdf}
  \caption{Cyber and regular fraud trends over age, income, education and unemployment.}
  \label{demographics}
\end{figure}
To evaluate the effect of prominent demographic features we perform a logistic regression for both cyber and regular complaint rates. Table \label{regressions} summarizes our coefficients and their significance. Among ethnicities, our results generate statistically significant results for only Hispanic communities. While the coefficients suggest that frauds decrease for heavier concentrations of  Hispanics, a survey study \cite{anderson2013consumer} showed that Hispanics and Black communities are more likely to be victims of crimes. The decreasing trend is actually a result of fraud underreporting due to cultural reasons, distrust in agencies the lack of awareness and education \cite{consumerlessons}.

Other socio economic variables that we take into account are age, income, education an the rate of unemployment. In addition to the regression analysis, we investigate their variation by observing complaint rates across their distributions in Figure \ref{demographics}.

@@

\textbf{Education:} Both cyber and regular complaints increase along with an increase in percentage education. We associate this trend with greater increased educational awareness among individuals \cite{consumerlessons}. Another subtle trend, in the increase in cyber to regular complaint ratio from 0.82 to 1.23. We associate this diverging trend to more educated individuals being active  the Internet  more frequently, and hence being more prone to online fraud{pewcollege}. Our reasoning is in line with insights from our regression analysis which additionally normalizes for other factors.

@@

\section{Discussion}\label{discussion}
Based on our findings from section \ref{eval}, we elaborate some discussion points in hopes that they will assist in the development of better policies and will help prevent consumer fraud in the U.S.

@@

We also learn that fraudulent entities tend to work in groups and establish networks \cite{buffalodebt2}. The fraudulent cyber establishments of San Jose and San Francisco discussed in section \ref{fraudsters}, help us understand that fraudulent entities use strategic measures to gel-in with the legitimate industry. This necessitates the need for stricter policies while registering organizations with the State agencies. Localization of fraudsters also allows inspection teams to target efficiently. 
By observing overlap between top cyber and regular frauds (Table \ref{topfrauds}) we realize that with the rise of Internet, fraudsters have their methodologies to execute scams on the Internet that were initially perpetrated through regular methods. We suggest that policy makers should work closely with technologists to devise advanced learning mechanisms similar to \cite{brause1999neural, moreau1997detection} which enables the filtering and control of fraud.

\section{Conclusion and Future Work}\label{conclusion}

The goal of this paper is to provide a comprehensive comparison of cyber and regular consumer fraud in the United States. By applying an efficient classification and measurement methodology on an FTC complaint dataset, we explore trends among cyber and regular fraud, in time, distance and location metrics as well as their variation across consumer demographics. Based on our findings, we suggest insights to aid policy development for fraud prevention. In future, we look forward to working closely with regulatory organizations and provide data driven policy insights.

>>>>

\begin{figure}[b]
\centering
  \includegraphics[scale=0.29]{graphics/demographics.pdf}
  \caption{Cyber and regular fraud trends over age, income, education and unemployment.}
  \label{demographics}
\end{figure}
To evaluate the effect of prominent demographic features we perform a logistic regression for both cyber and regular complaint rates. Table \label{regressions} summarizes our coefficients and their significance. Among ethnicities, our results generate statistically significant results for only Hispanic communities. While the coefficients suggest that frauds decrease for heavier concentrations of  Hispanics, a survey study \cite{anderson2013consumer} showed that Hispanics and Black communities are more likely to be victims of crimes. The decreasing trend is likely a result of fraud under-reporting due to cultural reasons, distrust in institutions, and lack of awareness or education \cite{consumerlessons}.

Other socio-economic variables that we take into account are age, income, education an the rate of unemployment. In addition to the regression analysis, we investigate their variation by observing complaint rates across their distributions in Figure \ref{demographics}.

@@

\textbf{Education:} Both cyber and regular complaints increase along with an increase in percentage education. We associate this trend with greater increased educational awareness among individuals \cite{consumerlessons}. Another subtle trend, in the increase in cyber to regular complaint ratio from 0.82 to 1.23. We associate this diverging trend to more educated individuals being active  the Internet  more frequently, and hence being more prone to online fraud~\cite{pewcollege}. Our reasoning is in line with insights from our regression analysis which additionally normalizes for other factors.

@@

\section{Discussion}\label{discussion}
Based on our findings from section \ref{eval}, we elaborate some discussion points to provide context for this analysis in hopes that it will assist in the development of better policies and help reduce consumer fraud in the U.S.

@@

We also learn that fraudulent entities tend to work in groups and establish networks \cite{buffalodebt2}. The fraudulent cyber establishments of San Jose and San Francisco discussed in Section \ref{fraudsters}, help us understand that fraudulent entities likely reflect the makeup of nearby  legitimate industries.  
By observing the overlap between top cyber and regular frauds (Table \ref{topfrauds}) we realize that with the rise of Internet, fraudsters have their choice of vectors to execute scams  that were traditionally only perpetrated through traditional means. Better understanding these advanced communication  modalities requires a technologists' touch;  policy makers should consider working closely with technologists to devise detection mechanisms similar to \cite{brause1999neural, moreau1997detection} which enable better filtering and control of fraudulent activity.

\section{Conclusion}\label{conclusion}

The goal of this paper is to investigate the dynamics of cyber and traditional methods for committing  fraud in the United States. By partitioning the FTC Consumer Sentinel complaint dataset, we are able to explore trends among cyber and regular fraud, and analyze trends along time, distance and location metrics as well as their variation across consumer demographics. While the Internet has greatly expanded the potential reach and scale of fraudsters: where once they could only use mail or telephones for various frauds, the Internet enables one to contact millions of users very quickly, whether through fraudulent websites, Craigslist posts, or spam emails. Even so, the difference between the cyber and non-cyber methodologies is not overwhelming: this effect suggests that non-cyber activities, like purchasing goods or posting money orders, may still serve as a limiting factor on the extent or targeting of these fraudulent activities.
